When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-11-27 doc/paper/vpd_et_paper.tex
finished first paragraph of testing theory; should now flow with current text and probably just needs editing

\subsection{Full observations of $\frac{\partial \; ET}{\partial \; D}$}

Now that we have an intuitive understanding of $\frac{\partial \; ET}{\partial \; D}$'s behavior, we are equipped to interpret fully realistic plots of $\frac{\partial \; ET}{\partial \; D}$ for each PFT. Figure \ref{real} presents calculated $\frac{\partial \; ET}{\partial \; D}$ where, unless otherwise noted, all variables in Equation \ref{d_et} are allowed to vary. Each column is a different quantity related to $\frac{\partial \; ET}{\partial \; D}$, and each row is a different PFT.

The full observations generally confirm expectations from Section \ref{results}. CRO has the most positive values of $\frac{\partial \; ET}{\partial \; D}$, $\frac{\partial \; ET}{\partial \; D}$ is almost always negative for CSH, and response depends more with the environmental conditions for the other PFTs (especially ENF). Through the columns of Figure \ref{real} we can see the impact of $\sigma$ and $g_a$ on the variability of $\frac{\partial \; ET}{\partial \; D}$. $g_a$'s scaling (included in columns 1 and 3) alters the magnitude considerably. $\sigma$ variability (included in columns 1 and 2) adds a lot of additional noise to the signal of $\frac{\partial \; ET}{\partial \; D}$, which is slightly undesirable given $\sigma$'s role in representing model and observational uncertainty. However, the general story with the noise appears to match the cleaner signal when $\sigma$ is help constant and $D_{ETmin}$ is clearly visible \explain{I really need to make these plots better - way too much overlapping of points that hurts the story}. One exception is possibly with GRA, for which uncertainty represented in $\sigma$ is high and causes the full complexity plots (Columns 1 and 2) to not match well with $\sigma$ held fixed (Columns 3 and 4).

>>>>

\subsection{Testing the theory - does the data match the model?}

So far we have developed a theory for $\frac{\partial \; ET}{\partial \; D}$'s behavior. In particular, we determined a critical threshold $D_{crit}$ for $\frac{\partial \; ET}{\partial \; D}$. For $D < D_{crit}$, $\frac{\partial \; ET}{\partial \; D}  < 0$, and for $D > D_{crit}$, $\frac{\partial \; ET}{\partial \; D} > 0$. This $D_{crit}$ is only a function of PFT. However, many assumptions, including constant uWUE, were made in deriving $D_{crit}$. So, we need to test if our theory and $D_{crit}$ hold up in the face of uncertainty. Figure \ref{real} presents calculated $\frac{\partial \; ET}{\partial \; D}$ where, unless otherwise noted, all variables in Equation \ref{d_et} are allowed to vary, including uncertainty. Each column is a different quantity related to $\frac{\partial \; ET}{\partial \; D}$, and each row is a different PFT.

The full observations generally confirm expectations from Section \ref{results}. CRO has the most pospitive values of $\frac{\partial \; ET}{\partial \; D}$, $\frac{\partial \; ET}{\partial \; D}$ is almost always negative for CSH, and response depends more with the environmental conditions for the other PFTs (especially ENF). Through the columns of Figure \ref{real} we can see the impact of $\sigma$ and $g_a$ on the variability of $\frac{\partial \; ET}{\partial \; D}$. $g_a$'s scaling (included in columns 1 and 3) alters the magnitude considerably. $\sigma$ variability (included in columns 1 and 2) adds a lot of additional noise to the signal of $\frac{\partial \; ET}{\partial \; D}$, which is slightly undesirable given $\sigma$'s role in representing model and observational uncertainty. However, the general story with the noise appears to match the cleaner signal when $\sigma$ is help constant and $D_{ETmin}$ is clearly visible \explain{I really need to make these plots better - way too much overlapping of points that hurts the story}. One exception is possibly with GRA, for which uncertainty represented in $\sigma$ is high and causes the full complexity plots (Columns 1 and 2) to not match well with $\sigma$ held fixed (Columns 3 and 4).
